Physcraper: a python package for continual update of evolutionary estimates using the Open Tree of Life

### 2020-08-13 docs/submission-mee-2020-08-12.tex
updating pdf

\begin{figure}
\includegraphics[width=1\linewidth]{docs/figs/ilex-plot-tips-and-branches-1} \caption{Physcraper outpus tree obtained by updating the alignment from Gottlieb *et al.* 2005}\label{fig:ilex-updated-tree}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{docs/figs/ilex-plot-tips-and-branches-1} \caption{A phylogenetic tree is the main result of a Physcraper analysis. In this example, Physcraper updated an alignment of 48 samples of the genus Ilex from Gottlieb et al. 2005 (black tips) and added 222 new samples from the GenBank database (red tips), corresponding to 78 new taxa, aligned the new seqeunces to the original alignment using MUSCLE and performed the phylogenetic reconstruction using RAxML.}\label{fig:ilex-updated-tree}
\end{figure}
